Model

### 2019-08-21 stats/model.Rmd
update code

me_data <- read_csv("../data/child_basic_me.csv")

@@

# 3 chains, 6000 iterations per chain, 2000 burn in, lag = 1
sem_know_model <- readRDS("../saves/run_correlations.rds")#%>%
  # filter(Chain != "15",
  #        Chain != "1",
  #        Chain != "30",
  #        Chain != "6",
  #        Chain != "5",
  #        Chain != "7",
  #        Chain != "3")

@@

@@

ggsave("../graphs/so_by_chain.pdf", width = 4, height = 3, scale = 1.5)
```

@@

sem_know_cor_params  <- readRDS("../saves/run_correlations.rds")%>%
  separate(Parameter, into = c("parameter", "type","item"), sep = ",")%>%
  filter(parameter == "parameter", type == "items")%>%
  separate(value, into = c("int", "slope"),sep = ", ")%>%
  mutate(int = as.numeric(str_remove_all(int, "[(c]")),
         slope = as.numeric(str_remove(slope, "[)]")))%>%
  gather(parameter, value, int, slope)
 # %>%
#   filter(Chain != "15",
#          Chain != "1",
#          Chain != "30",
#          Chain != "6",
#          Chain != "5",
#          Chain != "7",
#          Chain != "3")

@@

ggsave("../graphs/item_by_chain.pdf", width = 15, height = 15, scale = 1.5)
```

@@

ggsave("../graphs/corr_int_by_age.pdf", width = 5, height = 4, scale = 1.5)

@@

inv_model_data <- item_params_summary%>%
  select(-uci,-lci)%>%
  spread(parameter, mode)%>%
  expand(item, int,slope,age = unique(me_model_data$age- min(me_model_data$age)))%>%
  mutate(so_int = global_params_summary%>%filter(token == "speaker_optimality", parameter == "int")%>%pull(mode),
         so_slope = global_params_summary%>%filter(token == "speaker_optimality", parameter == "slope")%>%pull(mode))%>%
  mutate(speaker_optimality = so_int + so_slope * age,
         semantic_knowledge = plogis(int + slope * age))

@@

```{r}
p2 <- read_csv("../data/child_basic_me.csv")%>%
  filter(trial != "train1",
         trial != "train2")%>%
  mutate(item = familiar)%>%
    left_join(aoa_ratings)%>%
  ungroup()%>%
  mutate(familiar = fct_reorder(factor(item), mean_aoa))

@@

novel_data <- read_csv("../data/child_spin_novelty.csv")%>%
  mutate(age_num = age_num-min(age_num))

>>>>

me_data <- read_csv("../data/me.csv")

@@

# 3 chains, 6000 iterations per chain, 2000 burn in, lag = 1
sem_know_model <- readRDS("../saves/run_correlations.rds")%>%
  filter(Chain != "15",
         Chain != "1",
         Chain != "30",
         Chain != "6",
         Chain != "5",
         Chain != "7",
         Chain != "3")

@@

```{r}
me_model_data <- read_csv("../data/me.csv")%>%
    filter(trial != "train1",
           trial != "train2")%>%
  mutate(age = age_num - min(age_num))

@@

#ggsave("../graphs/so_by_chain.pdf", width = 4, height = 3, scale = 1.5)
```

@@

sem_know_cor_params  <- readRDS("../saves/run_correlations.rds")%>%
  separate(Parameter, into = c("parameter", "type","item"), sep = ",")%>%
  filter(parameter == "parameter", type == "items")%>%
  separate(value, into = c("int", "slope"),sep = ", ")%>%
  mutate(int = as.numeric(str_remove_all(int, "[(c]")),
         slope = as.numeric(str_remove(slope, "[)]")))%>%
  gather(parameter, value, int, slope)

sem_know_cor_params <- sem_know_cor_params%>%
  filter(Chain != "15",
         Chain != "1",
         Chain != "30",
         Chain != "6",
         Chain != "5",
         Chain != "7",
         Chain != "3")

@@

#ggsave("../graphs/item_by_chain.pdf", width = 15, height = 15, scale = 1.5)
```

@@

#ggsave("../graphs/corr_int_by_age.pdf", width = 5, height = 4, scale = 1.5)

@@

inv_model_data <- item_params_summary%>%
  select(-uci,-lci)%>%
  spread(parameter, mode)%>%
  tidyr::expand(item, int,slope,age = unique(me_model_data$age- min(me_model_data$age)))%>%
  mutate(so_int = global_params_summary%>%filter(token == "speaker_optimality", parameter == "int")%>%pull(mode),
         so_slope = global_params_summary%>%filter(token == "speaker_optimality", parameter == "slope")%>%pull(mode))%>%
  mutate(speaker_optimality = so_int + so_slope * age,
         semantic_knowledge = plogis(int + slope * age))

@@

```{r}
p2 <- read_csv("../data/me.csv")%>%
  filter(trial != "train1",
         trial != "train2")%>%
  mutate(item = familiar)%>%
    left_join(aoa_ratings)%>%
  ungroup()%>%
  mutate(familiar = fct_reorder(factor(item), mean_aoa))

@@

novel_data <- read_csv("../data/novelty.csv")%>%
  mutate(age_num = age_num-min(age_num))
